---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Lucas Fernandez Seivane"
date: "11 de febrero de 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Presentation for Developing Data Products

For the final project of Developing Data Products I selected a very simple project: visualization of the dataset of
the dataset of the Abalone Dataset and running a simple lineal regression. The dataset comes from
https://archive.ics.uci.edu/ml/datasets/abalone

## Description and application of the dataset
Abalone is a mollusc with high importance in acquiculture and gastronomy. Predicting the viability
and optimizing the (slow) growth of specimens means the viability or the bankrrupcy of a company.

```{r abalone, echo = TRUE}
abalone <- read.csv(
  "http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data", 
                    header = FALSE)
names(abalone) <- c("sex", "length", "diameter", "height", "weight.whole",
                    "weight.shucked", "weight.viscera", "weight.shell", "rings")
```
## Data summary
```{r, echo = TRUE}
summary(abalone)
```


## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

